rowing: analysis of sculls in the 2016 Olympics

### 2021-11-09 inst/rowing.Rmd
consistency check
add hex sticker to more Rmd files
minor typesetting

This short document analyses the `rowing` dataset: sculls in the 2016
olympics.  It is not really standalone and is here as part of a
consistent dataset generation mechanism used in the `hyper2` package.
See the `hyper2` vignette for a more formal discussion.  In Olympic
sculling, up to six individual competitors race a small boat called a
scull over a course of length 2\,km; the object is to cross the
finishing line first.  Note that actual timings are irrelevant, given
the model, as the sufficient statistic is the order in which
competitors cross the finishing line.  The 2016 Summer Olympics is a
case in point: the gold and silver medallists finished less than~5
milliseconds apart, corresponding to a lead of~$\sim
2.5\,\mathrm{cm}$.  The dataset is as follows;

@@

>>>>

<p style="text-align: right;">
![](`r system.file("help/figures/hyper2.png", package = "hyper2")`){width=10%}
</p>

This short document analyses the `rowing` dataset: sculls in the 2016
olympics.  It is not really standalone and is here as part of a
consistent dataset generation mechanism used in the `hyper2` package.
See the `hyper2` vignette for a more formal discussion.  In Olympic
sculling, up to six individual competitors race a small boat called a
scull over a course of length $2\,\mathrm{km}$; the object is to cross
the finishing line first.  Note that actual timings are irrelevant,
given the model, as the sufficient statistic is the order in which
competitors cross the finishing line.  The 2016 Summer Olympics is a
case in point: the gold and silver medallists finished less than $\sim
5$ milliseconds apart, corresponding to a lead of $\sim
2.5\,\mathrm{cm}$.  The dataset is as follows;

@@

```{r conscheck, cache=TRUE,fig.cap="consistency check for rowing function"}
consistency(rowing)
```
